EvoSwarm: An Event-based Architecture for Multi-population Optimization Algorithms

### 2020-05-14 draft.tex
References to sections corrected.

We have proved this in the following steps:
% The reviewer says that we should clarify the contributions, and the
% contribution should answer a research question. Maybe we should
% clarify these contributions to answer to that. Contribution should
% be something like "We have proved that cloud-native applications are
% able to easily accommodate multi-paradigm bioinspired algorithms
% with little efforts of parametrization and
% that a combination of algorithms has better speedup and performance
% than any single one taken independently.
% These items above could be preceded by "We have proved this in the
% following steps" - JJ
% I like it will put it just like that. 
% A reviewer also put enphasis on the workflow and reproductivility 
% and extracting a Model? we can put something on that too.
% yep.

% Maybe here you should make reference to the sections where you are actually doing it (after conveniently rephrasing it) - JJ
\begin{itemize}
    \item First, we present the design and implementation of a reactive 
    container-based application for the asynchronous execution of multi-population 
    algorithms. The source code and example container definitions are
    publicly available. % Not really a contribution. It's the mean to
    % achieve the contribution - JJ
    % Maybe you should check this out again ... - JJ
    \item Second, we propose a method for the deployment and execution of 
    multiple experiments by specifying the infrastructure as part of an 
    experiment definition in both local or cloud environments,
    facilitating the reproduction of experimental results. % Not clear
                                % what the contribution is. If this
                                % has been used for the first time in
                                % an EA environment, it should be
                                % stated that way. If not, it's also a
                                % mean to achieve the contribution - JJ
    \item Third, the application is compatible with the COCO benchmark 
    framework, allowing researchers to compare the performance of their 
    algorithms with other works. % Not really a contribution, but an
                                % implementation detail. Convenient,
                                % but does not advance the state of
                                % the art - JJ
    \item Fourth, we present an empirical study to validate the 
    applicability of our application,  measuring the execution time and  
    speedup.

@@

The organization of the paper is as follows: First, in Section \ref{multi}, we present a
background of the fundamental issues of integrating nature-inspired optimization
and multi-population methods. Section \ref{soa} presents state of the art relevant to
our work. In Section \ref{method}, we present the proposed method and the container-based
application in Section \ref{docker} . % No reference to section 6.
Section \ref{setup} describes
the design of the empirical evaluation we designed to assess the effectiveness
of the method, and in Section \ref{results}, % This is a subsection, fix it. 
we report and discuss the results. % No references to sections 9 and 10
Finally, we
offer the conclusions of this paper and suggestions on future work in Section \ref{conclusions}.

@@

\section{Deploying to a cloud provider}

Container-based applications describe the deployment of loosely coupled
processes in a consistent and portable way, in every phase of the life cycle of
an application, from development through testing to production independently on
the kind of infrastructure. The term cloud-native describes these
container-based environments because they are deployed on an infrastructure that
abstracts the underlying compute, storage, and networking primitives. This
infrastructure does need to be a cloud provider; it could be a developer's
laptop, a single server, or a production environment. When we deploy a
cloud-native application to a cloud provider, we have some more options to
choose:

>>>>

We have proved this in the following steps:
% The reviewer says that we should clarify the contributions, and the
% contribution should answer a research question. Maybe we should
% clarify these contributions to answer to that. Contribution should
% be something like "We have proved that cloud-native applications are
% able to easily accommodate multi-paradigm bioinspired algorithms
% with little efforts of parametrization and
% that a combination of algorithms has better speedup and performance
% than any single one taken independently.
% These items above could be preceded by "We have proved this in the
% following steps" - JJ
% I like it will put it just like that. 
% A reviewer also put enph   asis on the workflow and reproductivility 
% and extracting a Model? we can put something on that too.
% yep.

% Maybe here you should make reference to the sections where you are actually doing it (after conveniently rephrasing it) - JJ
\begin{itemize}
    \item First, we present the design and implementation of a reactive 
    container-based application for the asynchronous execution of multi-population 
    algorithms. The source code and example container definitions are
    publicly available. % Not really a contribution. It's the mean to
    % achieve the contribution - JJ
    % Maybe you should check this out again ... - JJ
    \item Second, we propose a new method for the deployment and execution of 
    multiple experiments by specifying the infrastructure as part of an 
    experiment definition in both local or cloud environments,
    facilitating the reproduction of experimental results. % Not clear
                                % what the contribution is. If this
                                % has been used for the first time in
                                % an EA environment, it should be
                                % stated that way. If not, it's also a
                                % mean to achieve the contribution - JJ
    \item Third, the application is compatible with the COCO benchmark 
    framework, allowing researchers to compare the performance of their 
    algorithms with other works. % Not really a contribution, but an
                                % implementation detail. Convenient,
                                % but does not advance the state of
                                % the art - JJ
    \item Fourth, we present an empirical study to validate the 
    applicability of our application,  measuring the execution time and  
    speedup.

@@

The organization of the paper is as follows: First, in Section \ref{multi}, we present a
background of the fundamental issues of integrating nature-inspired optimization
and multi-population methods. Section \ref{soa} presents state of the art relevant to
our work. In Section \ref{method}, we present the proposed method and the container-based
application in Section \ref{docker} and the workflow for experiment design in Section \ref{experiment_flow}. % No reference to section 6.
Section \ref{setup} describes
the design of the empirical evaluation we designed to assess the effectiveness
of the method, scalability is analysed in Section \ref{sec:exp1}, % This is a subsection, fix it. 
the performance of heterogeneous populations in Second \label{sec:exp2} 
and a cloud deployment example in Section \ref{cloud-aws}. % No references to sections 9 and 10
Finally, we
offer the conclusions of this paper and suggestions on future work in Section \ref{conclusions}.

@@

\section{Deploying to a cloud provider}
\label{cloud-aws}
Container-based applications describe the deployment of loosely coupled
processes in a consistent and portable way, in every phase of the life cycle of
an application, from development through testing to production independently on
the kind of infrastructure. The term cloud-native describes these
container-based environments because they are deployed on an infrastructure that
abstracts the underlying compute, storage, and networking primitives. This
infrastructure does need to be a cloud provider; it could be a developer's
laptop, a single server, or a production environment. When we deploy a
cloud-native application to a cloud provider, we have some more options to
choose:
